---
title: "R Notebook"
output: html_notebook
---

Load the lib (you might want to install it first).

```{r}
library(bibliometrix)   ### load bibliometrix package
library(htmlwidgets) # to have saveWidget
library(data.table) # for the sources tables
```

Import the wos and scopus publication files.

```{r}
file_wos <- "wos_2018_2023.bib"
file_scopus <- "scopus_2018_2024.bib"
M_wos <- convert2df(file = file_wos, dbsource = "wos", format = "bibtex")
M_scopus <- convert2df(file = file_scopus, dbsource = "scopus", format = "bibtex")
```

First bibliometric analysis:
```{r}
results_wos <- biblioAnalysis(M_wos, sep = ";")
results_scopus <- biblioAnalysis(M_scopus, sep = ";")
write.csv(results_wos$Sources, "sources_wos.csv", row.names=FALSE)
write.csv(results_scopus$Sources, "sources_scopus.csv", row.names=FALSE)
```

Basic plots for WoS data.
```{r}
plot(x = results_wos, k = 10, pause = FALSE)
```
Basic plots for Scopus data.
```{r}
plot(x = results_scopus, k = 10, pause = FALSE)
```
Some citation analysis with WoS data.
```{r}
CR <- citations(M_wos, field = "article", sep = ";")
cbind(CR$Cited[1:10])
A <- cocMatrix(M_wos, Field = "SO", sep = ";")
sort(Matrix::colSums(A), decreasing = TRUE)[1:10]
```

```{r}
A <- cocMatrix(M_wos, Field = "CR", sep = ".  ")
sort(Matrix::colSums(A), decreasing = TRUE)[1:10]
```
The main sources for publication according to WoS data:
```{r}
data.table(results_wos$Sources)
```
The main sources for publication according to Scopus data:
```{r}
data.table(results_scopus$Sources)
```

Create keyword co-occurrences network with WoS data:
```{r}
NetMatrix <- biblioNetwork(M_wos, analysis = "co-occurrences", network = "keywords", sep = ";")
# Plot the network
net=networkPlot(NetMatrix, normalize="association", weighted=T, n = 25, Title = "WoS Keyword Co-occurrences", type = "fruchterman", size=T, edgesize = 4,labelsize=1.0,community.repulsion = 0.1,size.cex = T,halo = F)
```
Create keyword co-occurrences network with Scopus data:
```{r}
NetMatrix <- biblioNetwork(M_scopus, analysis = "co-occurrences", network = "keywords", sep = ";")
# Plot the network
net=networkPlot(NetMatrix, normalize="association", weighted=T, n = 20, Title = "Scopus Keyword Co-occurrences", type = "fruchterman", size=T, edgesize = 4,labelsize=1.0,community.repulsion = 0.1,size.cex = T,halo = F)
```

Create classical article coupling network with WoS data:
```{r}
NetMatrix <- biblioNetwork(M_wos, analysis = "coupling", network = "references", sep = ";")
# Plot the network
net=networkPlot(NetMatrix,  normalize = "salton", weighted=NULL, n = 30, Title = "WoS Article' Coupling", type = "fruchterman", size=10,size.cex=T,remove.multiple=TRUE,labelsize=1.0,label.n=20,label.cex=F)
```
Create authors' coupling network with WoS data:
```{r}
NetMatrix <- biblioNetwork(M_wos, analysis = "coupling", network = "authors", sep = ";")
net=networkPlot(NetMatrix,  normalize = "salton", weighted=T, n = 20, Title = "WoS Authors' Coupling", type = "fruchterman", size = 5,size.cex=T,remove.multiple=TRUE,labelsize=2.0,label.n=20,label.cex = T)
```
Conceptual Structure using keywords (method="CA") with WoS data:
```{r}
options(ggrepel.max.overlaps = Inf)
CS <- conceptualStructure(M_wos,field="ID", method="CA", minDegree=4, clust=5, stemming=FALSE, labelsize=10, documents=10)
```
Conceptual Structure using keywords (method="CA") with Scopus data:
```{r}
CS <- conceptualStructure(M_scopus,field="ID", method="CA", minDegree=4, clust=5, stemming=FALSE, labelsize=10, documents=10)
```
Create a historical citation network with WoS data:
```{r}
options(width=200)
histResults <- histNetwork(M_wos, min.citations = 1, sep = ";")
# Plot a historical co-citation network
net <- histPlot(histResults, n=20, size = 10, labelsize=5)
```

Read the synonym and ignored keywords files.
```{r}
#synonyms_file <- read.csv("synonyms.csv")
synonyms_file <- scan("synonyms.csv",sep='\n', what = "", quiet = TRUE)
synonyms_file <- gsub(",", "; ", synonyms_file)
synonyms_file <- c(synonyms_file)
remove_file <- scan("remove.csv",sep='\n', what = "", quiet = TRUE)
remove_file <- remove_file
```

Now, create the thematic map using the synonyms with WoS data:
```{r}
res <- thematicMap(M_wos, field = "ID", n = 250, minfreq = 5, size = 0.5, repel = TRUE, synonyms = synonyms_file, remove.terms = remove_file)
plot(res$map)
```

Now, create the thematic map using the synonyms and the author's keywords with WoS data:
```{r}
res <- thematicMap(M_wos, field = "DE", n = 250, minfreq = 5, size = 0.5, repel = TRUE, synonyms = synonyms_file, remove.terms = remove_file)
plot(res$map)
```

The same but with the Scopus data:
```{r}
res <- thematicMap(M_scopus, field = "ID", n = 250, minfreq = 5, size = 0.5, repel = TRUE, synonyms = synonyms_file, remove.terms = remove_file)
plot(res$map)
```

The same but with the Scopus data and the author's keywords:
```{r}
res <- thematicMap(M_scopus, field = "DE", n = 250, minfreq = 5, size = 0.5, repel = TRUE, synonyms = synonyms_file, remove.terms = remove_file)
plot(res$map)
```

We add the function to create wordlists.

```{r}
wordlist <- function(M, Field, n, measure, ngrams, remove.terms=NULL, synonyms=NULL){
  switch(Field,
         ID={v=tableTag(M,"ID", remove.terms  = remove.terms, synonyms = synonyms)},
         DE={v=tableTag(M,"DE", remove.terms = remove.terms, synonyms = synonyms)},
         TI={
           if (!("TI_TM" %in% names(M))){
             v=tableTag(M,"TI", ngrams=ngrams, remove.terms=remove.terms, synonyms = synonyms)
             
           }},
         AB={if (!("AB_TM" %in% names(M))){
           v=tableTag(M,"AB", ngrams=ngrams, remove.terms = remove.terms, synonyms = synonyms)
         }},
         WC={
           v=tableTag(M,"WC")
         }
  )
  names(v)=tolower(names(v))
  #v=tableTag(values$M,"ID")
  n=min(c(n,length(v)))
  Words=data.frame(Terms=names(v)[1:n], Frequency=(as.numeric(v)[1:n]), stringsAsFactors = FALSE)
  W=Words
  switch(measure,
         identity={},
         sqrt={W$Frequency=sqrt(W$Frequency)},
         log={W$Frequency=log(W$Frequency+1)},
         log10={W$Frequency=log10(W$Frequency+1)}
  )
  
  results=list(v=v,W=W, Words=Words)
  return(results)
}
```


```{r}
resW <- wordlist(M=M_wos, Field="ID", n=250, measure="identity", ngrams=1, synonyms = synonyms_file, remove.terms = remove_file)
W <- resW$W
write.csv(resW[["W"]], "data_wos.csv", row.names=FALSE)
Words <- resW$Words
w1 <- wordcloud2::wordcloud2(W, size = 1.5, minRotation = 0, maxRotation = 0, rotateRatio = 1)#minRotation = -pi/2, maxRotation = -pi/2)
saveWidget(w1, 'w1.html', selfcontained = T)
```

Wordcloud with WoS and keywords plus.
<iframe src = "w1.html" width = "1000" height = "1000"></iframe> 


```{r}
resW <- wordlist(M=M_wos, Field="DE", n=250, measure="identity", ngrams=1, remove.terms = remove_file, synonyms = synonyms_file)
W <- resW$W
write.csv(resW[["W"]], "data_wos_de.csv", row.names=FALSE)
Words <- resW$Words
w2 <- wordcloud2::wordcloud2(W, size = 1.5, minRotation = 0, maxRotation = 0, rotateRatio = 1)#minRotation = -pi/2, maxRotation = -pi/2)
saveWidget(w2, 'w2.html', selfcontained = T)
```

Wordcloud with WoS and author's keywords.
<iframe src = "w2.html" width = "1000" height = "1000"></iframe> 


```{r}
resW <- wordlist(M=M_scopus, Field="ID", n=250, measure="identity", ngrams=1, remove.terms = remove_file, synonyms = synonyms_file)
W <- resW$W
write.csv(resW[["W"]], "data_scopus.csv", row.names=FALSE)
Words <- resW$Words
w3 <- wordcloud2::wordcloud2(W, size = 1.5, color = 'random-dark', minRotation = 0, maxRotation = 0, rotateRatio = 1)
saveWidget(w3, 'w3.html', selfcontained = T)
```

Wordcloud with Scopus and keywords plus.
<iframe src = "w3.html" width = "1000" height = "1000"></iframe> 

```{r}
resW <- wordlist(M=M_scopus, Field="DE", n=250, measure="identity", ngrams=1, remove.terms = remove_file, synonyms = synonyms_file)
W <- resW$W
write.csv(resW[["W"]], "data_scopus_de.csv", row.names=FALSE)
Words <- resW$Words
w4 <- wordcloud2::wordcloud2(W, size = 1.5, color = 'random-dark', minRotation = 0, maxRotation = 0, rotateRatio = 1)
saveWidget(w4, 'w4.html', selfcontained = T)
```

Wordcloud with Scopus and author's keywords.
<iframe src = "w4.html" width = "1000" height = "1000"></iframe> 

We are done!
